Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-12 paper/paper.tex
Connected plots
More plotting
Plot all the things

\section{Parallel Search}

\section{Experiments}

\begin{figure}[p]
    \includegraphics*[scale=0.7]{plots/33v-par-cumulative.pdf}
    \hfill
    \includegraphics*[scale=0.7]{plots/plain-par-cumulative.pdf}

>>>>

\section{Experiments with Parallel Search}

?? Hardware.

?? Datasets.

\subsection{Parallel Search is Better Overall}

\begin{figure}[p]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-cumulative-33ved.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-plain-connected.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-cumulative-33ve-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-sip.pdf}

    \caption{Cumulative performance.}

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-histogram-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-plain-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for unlabelled, undirected graphs.}
\end{figure}

\begin{figure}[t]
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-histogram-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33v-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for vertex-labelled graphs.}
\end{figure}

\begin{figure}[t]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-histogram-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure}

\begin{figure}[t]
    \includegraphics*[scale=0.7]{plots/33v-par-cumulative.pdf}
    \hfill
    \includegraphics*[scale=0.7]{plots/plain-par-cumulative.pdf}
